Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 overall.tex
Address #4

Figure~\ref{fig:core-hours-utilization} shows the number of core hours used by
ATLAS on Titan, from January 2016 to February 2017. During that period, ATLAS
consumed a total of 73.8M core hours, for an average of 7M hours a month, with a
minimum of 3.3M hours in April 2016 and a maximum 14.8M hours in February 2017.

>>>>

Figure~\ref{fig:core-hours-utilization} shows the number of core-hours used by
ATLAS on Titan, from January 2016 to February 2017. During that period, ATLAS
consumed a total of 73.8M core-hours, for an average of 7M hours a month, with a
minimum of 3.3M hours in April 2016 and a maximum 14.8M hours in February 2017.
